Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Full readthrough and small changes.

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10,kav14,kav14a}, local
environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric galaxies with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08,for12} utilises crowdsourced visual classifications
to measure galaxies in colour-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

@@

Image information from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

@@

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. GZH includes co-added images from GOODS at both 2-epoch and 5-epoch
    depths. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS \& COSMOS, GEMS \&
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).

@@

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r$-band Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
21,522~galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch - BDS

Images with simulated AGN were classified in the interface in an identical
manner and were evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
using the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

The images used for classification in GZH were colour-composite JPEGs made from
multi-band data. These were created following the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centres. The relative scalings of the filter bands were
chosen while trying to reproduce the colour appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided \hst{} images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the two. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
GOODS images were added into GZH later (in March 2015). These images made
use of the full four-band data by using the arithmetic mean of \Bband{} and
\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
the red channel.

@@

In some cases, we found that attempting to emphasise faint features in the
images resulted in the sky noise taking the appearance of brightly-coloured
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the colour images and a desaturation operation performed.
This masking procedure was effective in preserving the colour balance for
galaxies and retained the visibility of faint features, while reducing the colour
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

In addition to the primary \hst{} legacy imaging sample with coloured images
described as above, GZH also includes samples of \hst{} galaxy images with
different colour prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced colour
saturation, and the second has reversed the colours so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of colour features. The `recoloured' set enables an
alternative test of potential colour biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past... - BDS

@@

Redshifts for the GZH catalogue were compiled from a variety of sources. For each
galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalogue_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalogue of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogues and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogues are marked
with a flag in Table~\ref{tbl:catalogue_hst}.  If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
measurement with the smallest reported 1-$\sigma$ error was selected in each
case.
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The procedure for classifying an image in GZH followed a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
identifying whether the object at the centre of the image was a smooth galaxy,
a galaxy with a disk or other features, or a star/artifact. Subsequent
questions in the tree depended on the previous answer(s) given by the classifier; the
decision tree was designed so that every question relevant to
the morphology in the process of being identified was answered. Questions that were not
answered were implicitly assumed to be absent in the image --- for example, if
the classifier identified a galaxy as being smooth, they were not asked to count the
number of spiral arms. For every task, the classifier chose a single answer before
continuing to the next question; they also had the option to restart any
classification in-progress.

The GZH decision tree was designed to remain close to that used by GZ2 while
taking account of the likely differences in high redshift systems, and has four
broad sets of morphologies classified by the users.  The first set
identified stars or image artifacts (the result of either bad data or incorrect
identification as a galaxy by the ACS pipeline); in this case, the
classification process ended and no further questions were asked. The second
set was smooth galaxies, intended to select ellipticals/early-types;
volunteers also indicate the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which labeled the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

The number of independent classifications per subject collected by GZH was on
average higher than GZ1 or GZ2, due to both the increased complexity of the
decision tree and the relative difficulty of classifying images of small and
distant galaxies. Images from the \main{} AEGIS, GEMS, and GOODS data sets had
a median of 122~independent classifications per image. The remainder of the
images either had a later activation date (\main{} COSMOS, \simagn) or a lower
retirement limit (\stripe{} and \coadd). Images from these samples had a median
of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of images
from AEGIS, GEMS, and GOODS that were previously excluded from the original
sample due to cuts on blended and/or saturated objects and subsequently
confirmed as classifiable galaxies. The GZH site collected data until its
replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 using
the fourth version of the Galaxy~Zoo site and the same GZH decision tree.
The GZH project had a total of 10,349,357~classifications from
93,898~registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $w$ was 1 for the top 95\% of classifiers, as ranked by consistency.
For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
effectively zero for the bottom 1\% in the distribution function. Since
downweighting only occurs for the bottom few percent of classifiers (and an even smaller
percentage of the classifications), the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin11,wil13} were based on observations of galaxies in the SDSS,
which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the morphological distribution
were due to a redshift-dependent bias that affects image quality and
classification accuracy (\ie, galaxies of a given mass/size will appear smaller
and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
technique; its dependence in data quality is a potential problem for
\emph{both} automated and visual classifications, and must be addressed in
order to accurately measure demographics over any significant redshift range.

@@

\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
surface brightness ($\mu$; intrinsic) and redshift ($z$;
extrinsic).

@@

The objective is to use these data to predict, for a galaxy with a measured
\ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it
had been viewed at $z=0.3$. This predicted value is defined as the ``debiased''
vote fraction \ffeaturesdebiased, and is calculated by applying a correction to
the measured value of \ffeatures, determined by the $\zeta$ function described
in the following section. A reliable predicted value can be obtained so long as
the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
that is, for a given \ffeaturesz, there is exactly one corresponding value of
\ffeatures{} at $z=0.3$.

Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
\ffeaturesrest{} is \emph{not} always single-valued; hence, it is not
appropriate to correct galaxies that lie in certain regions of surface
brightness/redshift/\ffeatures{} space. These regions tend to have low
\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
These regions contain two morphological types of galaxies: the first set are
genuine ellipticals, which have low values of \ffeatures{} at both high and low
redshift. The second group are disks whose features become indistinct at high
redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
the value observed at high redshift is very low. This effect is strongest at
high $z$ and low $\mu$, where features become nearly impossible to discern in
the images (see top right panel of Figure~\ref{fig:f_vs_f}).

>>>>

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10,kav14a,kav14}, local
environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric galaxies with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08,for12} utilises crowdsourced visual classifications
to measure galaxies in colour-composite images. The efforts of more than
200,000~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15,sme16}.

@@

Image information from
multiple \hst{} surveys were combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog (ACS-GC) by 
\citet{gri12}. A summary of the key parameters of the ACS-GC is given in
Table~\ref{tbl:gzh_numbers}.

@@

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the Northern and Southern Hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. GZH includes co-added images from GOODS at both 2-epoch and 5-epoch
    depths. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ each for the north and south fieldss). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS \& COSMOS, GEMS \&
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).

@@

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r$-band Petrosian flux) and a magnitude brighter than $m_r < 17.77$.
21,522~galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial cut of 17.77~mag.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot} \citep{ste87}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch - BDS

Images with simulated AGN were classified in the interface in an identical
manner and were evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
using the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} used the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

The images used for classification in GZH were colour-composite JPEGs made from
multi-band data. These were created following the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centres. The relative scalings of the filter bands were
chosen to reproduce the colour appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided \hst{} images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the red and blue. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using differing
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
GOODS images were added into GZH in March 2015. The deeper images made
use of the full four-band data by using the arithmetic mean of \Bband{} and
\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
the red channel.

@@

In some cases, we found that attempting to emphasise faint features in the
images resulted in the sky noise taking the appearance of brightly-coloured
speckles. This impaired the aesthetics of the images and was considered a potential
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the colour images and a desaturation operation performed.
This masking procedure was effective in preserving the colour balance for
galaxies and retained the visibility of faint features, while reducing the colour
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

In addition to the primary \hst{} legacy imaging sample with coloured images
described as above, GZH also includes samples of \hst{} galaxy images with
different colour prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced colour
saturation, and the second has reversed the colours so that the blue and red
filters have exchanged places in the RGB image. The ``faded'' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of colour features. The ``recoloured'' set enables an
alternative test of potential colour biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past... - BDS

@@

Redshifts for the GZH catalogue were compiled from a variety of sources. For each
galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalogue of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogues and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogues are marked
with a flag in Table~\ref{tbl:catalog_hst}.  If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
measurement with the smallest reported 1-$\sigma$ error was selected in each
case.
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The procedure for classifying an image in GZH followed a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
identifying whether the object at the centre of the image was a ``smooth'' galaxy,
a galaxy with a disk or other features, or a star/artifact. Subsequent
questions in the tree depended on the previous answer(s) given by the classifier; the
decision tree was designed so that every question relevant to
the morphology in the process of being identified was answered. Questions that were not
answered were implicitly assumed to be absent in the image --- for example, if
the classifier identified a galaxy as being smooth, they were not asked to count the
number of spiral arms. For every task, the classifier chose a single answer before
continuing to the next question; they also had the option to restart any
classification in-progress.

The GZH decision tree was designed to be similar to that used by GZ2 while
taking account of the likely differences in the morphologies of high redshift galaxies. There are four
broad sets of morphologies classified by the users in GZH.  The first set
identified stars or image artifacts (the result of either bad data or incorrect
identification of an object as a galaxy by the ACS pipeline); in this case, the
classification process ended and no further questions were asked. The second
set was for ``smooth'' galaxies, intended to select ellipticals/early-types;
volunteers also indicate the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which labeled the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification 
had the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

The number of independent classifications per subject collected by GZH was on
average higher than GZ1 or GZ2, due to both the increased complexity of the
decision tree and the relative difficulty of classifying images of small and
distant galaxies. Images from the \main{} AEGIS, GEMS, and GOODS data sets had
a median of 122~independent classifications per image. The remaining
images had fewer classifications either due to a later activation date (\main{} COSMOS, \simagn) or a lower
retirement limit (\stripe{} and \coadd). Images from these samples had a median
of 46--48~classifications per image (Figure~\ref{fig:classification_hist}).

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of images
from AEGIS, GEMS, and GOODS that were previously excluded from the original
sample due to cuts on blended and/or saturated objects and subsequently
confirmed as classifiable galaxies. The GZH site collected data until its
replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 using
a new version of the Galaxy~Zoo site but the same GZH decision tree.
The GZH project finished with a total of 10,349,357~classifications from
93,898~registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $w$ was 1 for the top 95\% of classifiers as ranked by consistency.
For the bottom 5\% of classifiers, $w$ drops smoothly and is
effectively zero for the bottom 1\% of the distribution function. Since
downweighting only occurs for the bottom few percent of classifiers (and an even smaller
percentage of the classifications), the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin11,wil13} were based on observations of galaxies in the SDSS,
which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the morphological distribution
were due to a redshift-dependent bias that affects image quality and
classification accuracy (\ie, galaxies of a given mass/size will appear smaller
and dimmer at higher redshifts).  This bias is not unique to crowdsourcing
techniques; its dependence in data quality is a potential problem for
\emph{both} automated and visual classifications, and must be addressed in
order to accurately measure demographics over any significant redshift range.

@@

\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, \changes{and there is no obvious technique
for separating these into individual effects}. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
surface brightness ($\mu$; intrinsic) and redshift ($z$;
extrinsic).

@@

The objective is to use these data to predict, for a galaxy with a measured
\ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it
had been viewed at $z=0.3$. This predicted value is defined as the ``debiased''
vote fraction \ffeaturesdebiased, and is calculated by applying a correction to
the measured value of \ffeatures, determined by the $\zeta$ function described
in the following section (Equation~\ref{eqn:fzeta_mod}). A reliable predicted value can be obtained so long as
the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued;
that is, for a given \ffeaturesz, there is exactly one corresponding value of
\ffeatures{} at $z=0.3$.

Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
\ffeaturesrest{} is \emph{not} always single-valued; hence, it is not
appropriate to correct galaxies that lie in certain regions of surface
brightness/redshift/\ffeatures{} space. Such regions tend to have low
\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
These regions contain two morphological types of galaxies: the first set are
genuine ellipticals, which have low values of \ffeatures{} at both high and low
redshift. The second group are disks whose features become indistinct at high
redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
the value observed at high redshift is very low. This effect is strongest at
high $z$ and low $\mu$, where features become nearly impossible to discern in
the images (see top right panel of Figure~\ref{fig:f_vs_f}).
